\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\markboth{Acknowledgments}{Acknowledgments}
I would like to take this opportunity to express my gratitude to everyone who has been actively involved in my stay at University of Li\'ege. 

Firstly, I would like to thank Profs. Ludovic Noels and Thierry J. Massart for providing me an opportunity to pursue my doctoral research under their guidance. I would like to thank University of Li\'ege for providing a platform to develop my research capabilities.

I gratefully acknowledge the financial support from F.R.S-F.N.R.S. under the project number PDR T.0038.16. Computational resources have been provided by the supercomputing facilities of the Consortium des Équipements de Calcul Intensif en Fédération Wallonie Bruxelles (CÉCI) funded by the Fond de la Recherche Scientifique de Belgique (FRS-FNRS).

I am grateful to the members of the jury Professors Pierre G\'erard, Peter Berke, Eric B\'echet, Pierre Geurts, Anne Jung and Lars Beex for the time they spent reading and reviewing my work.

I am grateful to Bernard and Karim for helping and guiding me through the vast library of functions, which helped me begin my work. I would like to thank Van Dung for helping me constantly with the code. Thank you, Christophe, for providing all the inputs to help me move ahead with the work. I would also like to thank Dr. Ling Wu, Profs. Gilles Louppe, Stephane Bordas, Angelo Simone and Dr. Fariborz Ghavamian for all their inputs and suggestions during the course of my doctorate. 

Thank you, Julien, for being an amazing office-mate, for guiding me through all the annoying questions as a newbie and for letting me use your fridge. Thank you, Tianyu, Juan and Soumi for all the office ideas and scientific gossip. I would also like to thank all my colleagues and friends I have made over the years, sharing lunch, drinks, games and carr\'e: Miguel, Philippe, Clara, C\'edric, Jordi, Billy, Vivian, Akula, Kevin, L\'eonard, Vinayak, Xing Liang, Pierre-Louis, Chandan, Jenny, Yeshodhara, Darshini, Naveen, Shreya, Vinu, Anurag, Jocelyn, and all the cricket friends. I would also like to thank the past members of the department, colleagues who helped me in the initial days at Li\`ege.

I would like to thank my parents, appa and amma, without whose support and love, I would not have reached the stage I am at right now, to Megha, Hari, Avaneesh and my in-laws, Jyothi and Waheed, who keep me motivated to bring out my best, and finally, to Rowshni, my wife, who has kept me sane and has been a constant support, especially during the past couple of months of quarantine.
